Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-06 paper/manuscript/_intermediate_version/paper_revised_submission_april2021_apa.Rmd
rename writing folder structure

authornote: |
  The data and code that support the findings of this study are available at https://osf.io/cdhw4/.

@@

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

@@

To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / (hits + false alarms)), recall (hits / (hits + misses)), and F-score (the harmonic mean of precision and recall).  In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`. For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`. While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections. In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.  We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`.

We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending]. To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands. Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands. When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`. We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.

@@

As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and decreasing face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure Appendix \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}). We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).

@@

How does the child's context influence the social information in view? 
@bruner1985role discussed the role of children's activities in shaping the information present for learning. Following this idea, we investigated whether there were differences in access to faces and hands by the activity that the child was engaged in. This hypothesis seems intuitively appealing. Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime). 
We did not have access to annotations of activity. 
Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
These location annotations were only available for two children, S and A.
Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames. 
In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.

@@

```{r avgSizes, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Average size of poses, faces, and hands detected in the dataset as a function of age for each child in the dataset (each color = different child). Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range."}

@@

# General Discussion
Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age. First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015]. 
This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018]. 
We also found this to be true when restricting our analyses to full-field faces, suggesting this effect is not driven by a concurrent shift from more full-view to partial-views of faces.

We also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. 
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @long2021automated found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

@@

# Acknowledgements
Thanks to the creators of the SAYCam dataset who made this work possible and to Alessandro Sanchez for his contributions to the codebase. This work was funded by a Jacobs Foundation Fellowship to MCF, a John Merck Scholars award to MCF, and NSF #1714726 to BLL.

>>>>

# authornote: |
#   Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
# 
#   Enter author note here.

@@

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

To evaluate OpenPose's performance, we compared its detections to the manually-annotated gold set of frames, calculating precision (hits / (hits + false alarms)), recall (hits / (hits + misses)), and F-score (the harmonic mean of precision and recall).  In our data, for faces, the F-score was `r round(face_performance[3],2)`, with a precision of `r round(face_performance[1],2)` and recall of `r round(face_performance[2],2)`. For hands, the F-score was `r round(hand_performance[3],2)`, with a precision of `r round(hand_performance[1],2)` and recall of `r round(hand_performance[2],2)`. While face and hand detections showed moderately good precision, face detections were overall slightly more accurate than hand detections. In general, hand detections suffered from fairly low recall, indicating that OpenPose likely underestimated the proportion of hands in the dataset.  We also found that restricting our detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`).

We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending]. To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where which a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands. Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands. When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`. We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.

@@

As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and decreasing face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}). We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).

@@

How does the child's context influence the social information in view? 
@bruner1985role discussed the role of children's activities in shaping the information present for learning. Following this idea, we investigated whether there were differences in access to faces by the activity that the child was engaged in. This hypothesis seems intuitively appealing. Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime).

We did not have access to annotations of activity. 
Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
These location annotations were only available for two children, S and A.
Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames. 
In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room.

@@

```{r avgSizes, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "Average size of poses, faces, and hands detected in the dataset  between eyes in faces detected as a function of age for each child in the dataset (each color = different child). Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range."}

@@

# General Discussion
Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.

First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015]. 
This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018]. 
We also found this to be true when restricting our analyses to full-field faces, suggesting this effect is not driven by a concurrent shift from more full-view to partial-views of faces.

We also found an unexpectedly high proportion of hands in infants' view, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. 
Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. 
During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

@@

# Acknowledgements

### 2022-01-06 paper/manuscript/appendix.Rmd
rename writing folder structure

knitr::opts_chunk$set(echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r}
## Read in preprocessed data 
load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections

## all bounding boxes
load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries.RData'))

@@

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_with_centerall_detections.RData'))

# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
```

@@

```{r}
### Examine gold sample performance by child hands
load(here::here('data/preprocessed_data_2021/child_adult_hand_annotations_by_frame.RData'))

@@

```{r} 
### Load turk hand annotations with all bounding boxes (multiple dets per frame)
load(here::here('data/preprocessed_data_2021/hand_annotations_2020-01-29.RData'))

@@

```{r}
# with all thresholds
load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))

load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
```

@@

# without thresholds
load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections.RData"))

@@

    # mutate(face_eval_ketan_center = evaluate_detector(face_present_ketan, face_detected_center), hand_eval_ketan_center = evaluate_detector(hand_present_ketan, hand_detected_center)) 
```

```{r}
# add age day bins to gold_sample
load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE) # 182
max_age = max(all_vid_data$age_days, na.rm=TRUE) # 966
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

@@

```{r}
# Evaluating prfs in center detections is challenging because we ONLY have ground truth on the full image -- so it's not that informative.

# return_prf_short(gold_sample$hand_eval_ketan_center)
# return_prf_short(gold_sample$face_eval_ketan_center)
```

@@

```{r}
load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta

@@

# OpenPose Annotation Examples
```{r include=FALSE}
load(file = here::here('data/preprocessed_data_2021/goldset_category_annotations.RData'))

fp_face_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(face_eval_ketan == 'FP')

fp_hand_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(hand_eval_ketan == 'FP')

fn_face_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(face_eval_ketan == 'FN')

fn_hand_examples <- d %>%
  left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
  filter(face_eval_ketan == 'FN')

images_to_render =  fp_hand_examples
which_images = 'fp_hand_examples'

public_urls = unique(images_to_render$public_url)
img_names_short = unique(images_to_render$img_name)

dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)

  for (i in 1:length(public_urls)){
    this_image = image_read(public_urls[i])
    image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
  }

@@

```{r}
det_types = c('FP','FN')

render_examples = FALSE
if (render_examples == TRUE) {
for (det_type in det_types) {
  to_render_hands <- d %>%
    distinct(vid_name, frame, public_url) %>%
    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
    filter(hand_eval_ketan == det_type) %>%
    ungroup() %>%
    dplyr::sample_n(7)

  image_read(to_render_hands$public_url) %>%
    image_append(stack = FALSE) %>%
    image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))

  ###
    to_render_faces <- d %>%
    distinct(vid_name, frame, public_url) %>%
    left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
    filter(face_eval_ketan == det_type) %>%
    ungroup() %>%
    dplyr::sample_n(7)

  image_read(to_render_faces$public_url) %>%
    image_append(stack = FALSE) %>%
    image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))

}
}

@@

```{r density-op-fps, fig.width=6, fig.height=3}
load(here::here('data/preprocessed_data_2021/gold_sample_all_indiivdual_dets.RData'))
ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  +
  scale_y_reverse()

>>>>

knitr::opts_chunk$set(echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

```{r}
## Read in preprocessed data 
load(here::here('data/preprocessed_data_2022/all_vid_data_from_bbs_all_detections.RData')) # all detections

## all bounding boxes
load(file=here::here('data/preprocessed_data_2022/bounding_box_summaries.RData'))

@@

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2022/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_with_centerall_detections.RData'))

# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2022/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
```

@@

```{r}
### Examine gold sample performance by child hands
load(here::here('data/preprocessed_data_2022/child_adult_hand_annotations_by_frame.RData'))

@@

```{r} 
### Load turk hand annotations with all bounding boxes (multiple dets per frame)
load(here::here('data/preprocessed_data_2022/hand_annotations_2020-01-29.RData'))

@@

```{r}
# with all thresholds
load(here::here("data","preprocessed_data_2022","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))

load(here::here('data/preprocessed_data_2022/gold_sample_annotations2020-01-31.RData')) # human annotations
```

@@

# without thresholds
load(here::here("data","preprocessed_data_2022","gold_sample_from_bbs_2021_all_detections.RData"))

@@

```{r}
# add age day bins to gold_sample
load(file=here::here('data/preprocessed_data_2022/all_vid_data_from_bbs_all_detections.RData')) # all detections
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE) # 182
max_age = max(all_vid_data$age_days, na.rm=TRUE) # 966
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

@@

@@

```{r}
load(here::here('data/preprocessed_data_2022/saycam_metadata.RData')) # meta

@@

# OpenPose Annotation Examples
```{r include=FALSE}
# load(file = here::here('data/preprocessed_data_2022/goldset_category_annotations.RData'))

# fp_face_examples <- d %>%
#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
#   filter(face_eval_ketan == 'FP')
# 
# fp_hand_examples <- d %>%
#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
#   filter(hand_eval_ketan == 'FP')
# 
# fn_face_examples <- d %>%
#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
#   filter(face_eval_ketan == 'FN')
# 
# fn_hand_examples <- d %>%
#   left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
#   filter(face_eval_ketan == 'FN')
# 
# images_to_render =  fp_hand_examples
# which_images = 'fp_hand_examples'
# 
# public_urls = unique(images_to_render$public_url)
# img_names_short = unique(images_to_render$img_name)
# 
# dir.create(here::here("data/annotation_examples/", which_images),recursive = TRUE)
# 
#   for (i in 1:length(public_urls)){
#     this_image = image_read(public_urls[i])
#     image_write(this_image,here::here("data/annotation_examples/",which_images, img_names_short[i]))
#   }

@@

```{r}
# det_types = c('FP','FN')
# render_examples = FALSE
# if (render_examples == TRUE) {
# for (det_type in det_types) {
#   to_render_hands <- d %>%
#     distinct(vid_name, frame, public_url) %>%
#     left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
#     filter(hand_eval_ketan == det_type) %>%
#     ungroup() %>%
#     dplyr::sample_n(7)
# 
#   image_read(to_render_hands$public_url) %>%
#     image_append(stack = FALSE) %>%
#     image_write(paste0(here::here("data/annotation_examples/"), 'example_hands_', det_type,".png"))
#   
#   ###
#     to_render_faces <- d %>%
#     distinct(vid_name, frame, public_url) %>%
#     left_join(gold_sample %>% select(vid_name, frame, face_eval_ketan, hand_eval_ketan)) %>%
#     filter(face_eval_ketan == det_type) %>%
#     ungroup() %>%
#     dplyr::sample_n(7)
# 
#   image_read(to_render_faces$public_url) %>%
#     image_append(stack = FALSE) %>%
#     image_write(paste0(here::here("data/annotation_examples/"), 'example_faces_', det_type,".png"))
#   
# }
# }

@@

```{r density-op-fps, fig.width=6, fig.height=3}
load(here::here('data/preprocessed_data_2022/gold_sample_all_indiivdual_dets.RData'))
ddd <- gold_sample_all_dets %>% left_join(gold_sample %>% select(frame, vid_name, face_eval_ketan, hand_eval_ketan))

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse()
